---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# MortgageRefiOptimizer

<!-- badges: start -->
<!-- badges: end -->

MortgageRefiOptimizer computes optimal refinance rates for fixed rate mortgages from various financial parameters from Agarwal et al (2013; "Optimal Mortgage Refinancing: A Closed-Form Solution"). 

## Installation

``` r
devtools::install_github("ChandlerLutz/MortgageRefiOptimizer")
```

## Example

The main package function is `compute_optimal_refi_rates()`

- See `?compute_optimal_refi_rates` for function parameters and a description of the output. 

Reproduce Agarwal Table 1 for a $1M mortgage: 

```{r example}
library(MortgageRefiOptimizer)

df_optimal_rates <- compute_optimal_refi_rates(
  rho = 0.05, sigma = 0.0109, mu = 0.1, i_0 = 0.06,
  gamma_uppercase = 25, pi = 0.03, tau = 0.28,
  M = 1e06, F = 2000, f = 0.01, N = 30,
  itemize_mtg_pymts = TRUE
)

str(df_optimal_rates)
```

- The package tests reproduce Agarwal et al. (2013) tables 1 and 2. 
